\chapter{Project Plan}
The execution of the rotary climbing wall project is organized through a series of systematic activities, structured to align with the engineering process. This ensures a disciplined approach to the development, from conceptualization to prototype testing. Detailed cost and timeline estimates for each activity are provided in Appendix A.

\section{Literature Review}
This chapter explores the main physiological variables essential for rock climbing and effective training. Each individual attribute is defined and investigated in terms of past research and how it fits into the three main rock climbing disciplines.

\section{Technology Review}
This chapter explores the current technological landscape when it comes to advanced rotating climbing walls. Current products are reviewed to determine the key features for such a product. The insights gained will guide the development of the rotating climbing wall prototype, combining the most effective elements from market leaders.

\section{Compile Design Requirements}
A complete set of design requirements will be created for the rotary wall.

\section{Investigate Concepts for Rotating Wall}
Perform the engineering design process on the rotary wall. This will include creating a functional decomposition, identifying sub-systems with proposed concepts for each.

\section{Select Preferred concept} 
The concepts will each go through a rigours selection process and the concepts that meet all the design requirements, while being the simplest designs will be selected.

\section{Design Review}
The proposed design will undergo a thorough evaluation against the compiled design requirements to make sure that it meets all the necessary criteria and performance requirements.

\section{Generate and Finalize Design}
This phase involves refining the selected concept, finalizing technical drawings and preparing the design for the manufacturing process.

\section{Part Sourcing}
With the design completed, the next step is identifying suppliers, sourcing parts by getting quotes and placing orders for all the necessary parts and materials for the construction.

\section{Construct Prototype}
The prototype rotary climbing wall will be constructed meticulously, following the finalized design and making sure to adhere to all safety protocols.

\section{Compile Final Report}
A comprehensive report will be compiled, detailing the entire process. This report will serve as a detailed record of the project's development and outcomes. 

