\chapter*{Plagiarism Declaration}

I have read and understand the Stellenbosch University Policy on Plagiarism and the definitions of plagiarism and self-plagiarism contained in the Policy [Plagiarism: The use of the ideas or material of others without acknowledgement, or the re-use of one's own previously evaluated or published material without acknowledgement or indication thereof (self-plagiarism or text-recycling)].

I also understand that direct translations are plagiarism, unless accompanied by an appropriate acknowledgement of the source. I also know that verbatim copy that has not been explicitly indicated as such, is plagiarism.

I know that plagiarism is a punishable offence and may be referred to the University's Central Disciplinary Committee (CDC) who has the authority to expel me for such an offence.

I know that plagiarism is harmful for the academic environment and that it has a negative impact on any profession.

Accordingly, all quotations and contributions from any source whatsoever (including the internet) have been cited fully (acknowledged); further, all verbatim copies have been expressly indicated as such (e.g. through quotation marks) and the sources are cited fully.

I declare that, except where a source has been cited, the work contained in this assignment is my own work and that I have not previously (in its entirety or in part) submitted it for grading in this module/assignment or another module/assignment.
I declare that I have not allowed, and will not allow, anyone to use my work (in paper, graphics, electronic, verbal or any other format) with the intention of passing it off as his/her own work.

I know that a mark of zero may be awarded to assignments with plagiarism and also that no opportunity will be given to submit an improved assignment.
\vspace{1.5cm}

\vspace{1cm}

\begin{table}[H]
\centering
\small % Further reduce font size in the table if needed
\setlength{\tabcolsep}{4pt} % Reduce column padding for more compact table
\begin{tabular}{|p{0.7\textwidth}|p{0.3\textwidth}|}
\hline
& \\
Student Number & Signature \\ \hline
& \\
Initials and Surname & Date \\ \hline
\end{tabular}%
\end{table}

\newpage

\section*{AI Use Declaration}

\begingroup
\small % Reduce font size for the entire declaration

\begin{enumerate}
    \setlength\itemsep{0.5em} % Reduce spacing between items
    \item I am convinced and can support my claim that my assessment product is an indication of my own learning, knowledge, skills, and understanding.
    \item Where I have used AI tools for enhancing my own creation of ideas and words, I acknowledge that I have to declare it.
    \item Where I have used AI tools for generating new ideas, words, code, image-prompts for other AI image-generating tools, or structure and even presentations (or other AI tools that can be used as assistants to the knowledge-building and representing process), I have declared and documented the use of such tools and am prepared to talk about the process I used and what it contributed to my learning and insights.
    \item I am aware that the lecturer can ask me to demonstrate my learning, for example, by explaining the choices I made in terms of approach, content used, literature selected, conclusions drawn, etc., through an additional assessment, such as an oral exam.
    \item I understand that if I am not able to agree to the above points, there is a chance that my academic behavior will be deemed unethical and might lead to a disciplinary case being brought against me on the grounds of cheating or plagiarism, and that the standard procedures for such behavior will be followed.
    \item As per the Disciplinary Code of SU (par. 10.2.1 and 10.2.2), I understand that I take responsibility for the integrity of my work, which includes the obligation to ask for clarification from an academic member of staff if I am unsure of anything, and that I strictly adhered to all instructions received in the course of the academic assessment by relevant and authorized staff (whether the instruction is in oral or written format).
    \item I understand that when I am not able to document and declare my use of AI tools, this behavior will be deemed as cheating in examinations and assessments (Disciplinary Code 1.1~c.), as I referred to "unauthorized notes, books, electronic devices, or other reference material."
\end{enumerate}

\vspace{1cm}

\begin{table}[H]
\centering
\small % Further reduce font size in the table if needed
\setlength{\tabcolsep}{4pt} % Reduce column padding for more compact table
\begin{tabular}{|p{0.7\textwidth}|p{0.3\textwidth}|}
\hline
& \\
Student Number & Signature \\ \hline
& \\
Initials and Surname & Date \\ \hline
\end{tabular}%
\end{table}

\endgroup
