\section*{Executive summary}
\noindent
\rowcolors{2}{blue!5}{white}
\begin{longtable}{|p{\dimexpr \linewidth-2\tabcolsep-2\arrayrulewidth}|}
\hline%------------------------------------------------------------
\sumheading  Title of Project \\
\hline%------------------------------------------------------------
Development of a Rotary Climbing Wall \\[1ex]

\hline%------------------------------------------------------------
\sumheading  Objectives \\
\hline%------------------------------------------------------------
To design and prototype a rotary climbing wall to enable continuous and long-duration climbing, facilitating effective endurance training indoors.\\[1ex]

\hline%------------------------------------------------------------
\sumheading  What is current practice and what are its limitations? \\
\hline%------------------------------------------------------------
Current indoor climbing practices involve static walls with limited routes, which restrict continuous climbing and endurance training due to spatial constraints.  \\[1ex]

\hline%------------------------------------------------------------
\sumheading  What is new in this project? \\
\hline%------------------------------------------------------------
The project introduces a rotating wall mechanism that would function similarly to a vertical treadmill, allowing for uninterrupted climbing and customizable difficulty levels. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  If the project is successful, how will it make a difference? \\
\hline%------------------------------------------------------------
The successful implementation of this project will enable training devices such as this to be more accessible at a lower price.\\[1ex]

\hline%------------------------------------------------------------
\sumheading  What are the risks to the project being a success? Why is it expected to be successful? \\
\hline%------------------------------------------------------------
Risks involve the project becoming too expensive and being unable to be completed or viably built in the time available or within the allocated budged. 
\\[1ex]

\hline%------------------------------------------------------------
\sumheading  What contributions have/will other students made/make? \\
\hline%------------------------------------------------------------
This research project will serve to contribute to Stellenbosch University's knowledge and experience when it comes to rock climbing training techniques and equipment.
 \\[1ex]

\hline%------------------------------------------------------------
\sumheading  Which aspects of the project will carry on after completion and why? \\
\hline%------------------------------------------------------------
Further research may continue in optimizing the wall's design, exploring commercial production possibilities.\\[1ex]

\hline%------------------------------------------------------------
\sumheading  What arrangements have been/will be made to expedite continuation? \\
\hline%------------------------------------------------------------
 Documentation of design and development processes will be created in enough detail that the production demands and marketing potential can be assessed. \\[1ex]

\hline%------------------------------------------------------------
\end{longtable}

